Trend of Loglike

### 2017-10-03 analysis/Trend_of_loglike.Rmd
wflow_publish("Trend_of_loglike.Rmd")

@@

@@

@@

>>>>

```{r}
source('../code/lik.R')
source('../code/set_data.R')
source('../code/ash.R')
source('../code/mix.R')
source('../code/normalmix.R')
source('../code/mix_opt.R')
source('../code/output.R')
source('../code/ashutility.R')
```

@@

The estimated $\pi$ for $K=1：10$

```{r}
fit1$allmotif[[1]]$pi
fit1$allmotif[[2]]$pi
fit1$allmotif[[3]]$pi
fit1$allmotif[[4]]$pi
fit1$allmotif[[5]]$pi
fit1$allmotif[[6]]$pi
fit1$allmotif[[7]]$pi
fit1$allmotif[[8]]$pi
fit1$allmotif[[9]]$pi
fit1$allmotif[[10]]$pi
```

@@

The estimated $\pi$ for $K=1：10$

```{r}
fit2$allmotif[[1]]$pi
fit2$allmotif[[2]]$pi
fit2$allmotif[[3]]$pi
fit2$allmotif[[4]]$pi
fit2$allmotif[[5]]$pi
fit2$allmotif[[6]]$pi
fit2$allmotif[[7]]$pi
fit2$allmotif[[8]]$pi
fit2$allmotif[[9]]$pi
fit2$allmotif[[10]]$pi
```

@@

The estimated $\pi$ for $K=1：10$

```{r}
fit3$allmotif[[1]]$pi
fit3$allmotif[[2]]$pi
fit3$allmotif[[3]]$pi
fit3$allmotif[[4]]$pi
fit3$allmotif[[5]]$pi
fit3$allmotif[[6]]$pi
fit3$allmotif[[7]]$pi
fit3$allmotif[[8]]$pi
fit3$allmotif[[9]]$pi
fit3$allmotif[[10]]$pi
```
